### 2020-06-11 Analisis_y_Resultados/CMS_Actualizacion.tex

\begin{figure}[ht]
\centering
\includegraphics[width=1\textwidth]{Analisis_y_Resultados/imagenes/Momentum_resolution_of_Muon.png}
\caption{Comparación. Generados con python 2.7.}
%\label{Compara_sol_muon}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1\textwidth]{Analisis_y_Resultados/imagenes/Tracking_of_Muon.png}
\caption{Comparación. Generados con python 2.7.}
%\label{Compara_track_muon}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1\textwidth]{Analisis_y_Resultados/imagenes/Eficiencia_of_Muon.png}
\caption{Comparación. Generados con python 2.7.}
%\label{Compara_track_muon}
\end{figure}