### 2020-06-11 Simulacion/bad/Muones_por_Entradas.tex

\begin{figure}[ht]
\centering
\includegraphics[width=1\textwidth]{Simulacion/imagenes/Distribucion_Entries.png}
\caption{Estructura del proyecto de generación y diagrama de flujo de programación del mismo. Pagina del proyecto \url{https://github.com/franky8939/GeneradorDarkSUSY}}
\label{entradas1}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1\textwidth]{Simulacion/imagenes/Distribucion_Entries2.png}
\caption{Estructura del proyecto de generación y diagrama de flujo de programación del mismo. Pagina del proyecto \url{https://github.com/franky8939/GeneradorDarkSUSY}}
\label{entradas2}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1\textwidth]{Simulacion/imagenes/Distribucion_Entries3.png}
\caption{Estructura del proyecto de generación y diagrama de flujo de programación del mismo. Pagina del proyecto \url{https://github.com/franky8939/GeneradorDarkSUSY}}
\label{entradas3}
\end{figure}

\begin{landscape}
\begin{figure}[ht]
\centering
\includegraphics[width=1.3\textwidth]{Simulacion/imagenes/Comparacion_Distribucion_Entries.png}
\caption{Estructura del proyecto de generación y diagrama de flujo de programación del mismo. Pagina del proyecto \url{https://github.com/franky8939/GeneradorDarkSUSY}}
\label{entradas3}
\end{figure}
\end{landscape}