### 2020-06-11 link.tex

\newcommand{\fermion}{\href{https://es.wikipedia.org/wiki/Fermi\%C3\%B3n}{fermion}}
\newcommand{\fermiones}{\href{https://es.wikipedia.org/wiki/Fermi\%C3\%B3n}{fermiones}}

\newcommand{\boson}{\href{https://es.wikipedia.org/wiki/Bos\%C3\%B3n}{boson}}
\newcommand{\bosones}{\href{https://es.wikipedia.org/wiki/Bos\%C3\%B3n}{bosones}}

\newcommand{\fermidirac}{\href{https://es.wikipedia.org/wiki/Estad\%C3\%ADstica_de_Fermi-Dirac}{estadística de Fermi-Dirac}}

\newcommand{\boseeinstein}{\href{https://es.wikipedia.org/wiki/Estad\%C3\%ADstica_de_Bose-Einstein}{estadística de Bose-Einstein}}

\newcommand{\pauli}{\href{https://es.wikipedia.org/wiki/Principio_de_exclusi\%C3\%B3n_de_Pauli}{principio de exclusión de Pauli}}

\newcommand{\quark}{\href{https://es.wikipedia.org/wiki/Quark}{quark}}
\newcommand{\Quark}{\href{https://es.wikipedia.org/wiki/Quark}{Quark}}
\newcommand{\Quarks}{\href{https://es.wikipedia.org/wiki/Quark}{Quark}}
\newcommand{\quarks}{\href{https://es.wikipedia.org/wiki/Quark}{quarks}}

\newcommand{\lepton}{\href{https://es.wikipedia.org/wiki/Lept\%C3\%B3n}{lepton}}
\newcommand{\leptones}{\href{https://es.wikipedia.org/wiki/Lept\%C3\%B3n}{leptones}}
\newcommand{\Leptones}{\href{https://es.wikipedia.org/wiki/Lept\%C3\%B3n}{leptones}}

\newcommand{\hadron}{\href{https://es.wikipedia.org/wiki/Hadr\%C3\%B3n}{hadron}}
\newcommand{\hadrones}{\href{https://es.wikipedia.org/wiki/Hadr\%C3\%B3n}{hadrones}}

\newcommand{\matterspectrum}{\href{https://en.wikipedia.org/wiki/Matter_power_spectrum}{Harrison--Zeldovich}}

\newcommand{\Axion}{\href{https://en.wikipedia.org/wiki/Axion}{Axion}}
\newcommand{\axion}{\href{https://en.wikipedia.org/wiki/Axion}{axion}}
\newcommand{\Axiones}{\href{https://en.wikipedia.org/wiki/Axion}{Axiones}}
\newcommand{\axiones}{\href{https://en.wikipedia.org/wiki/Axion}{axiones}}

\newcommand{\neutralinos}{\href{https://en.wikipedia.org/wiki/Neutralino}{neutralinos}}
\newcommand{\neutralino}{\href{https://en.wikipedia.org/wiki/Neutralino}{neutralino}}

\newcommand{\WIMP}{\href{https://en.wikipedia.org/wiki/Weakly_interacting_massive_particles}{\textbf{WIMP}}}
\newcommand{\WIMPs}{\href{https://en.wikipedia.org/wiki/Weakly_interacting_massive_particles}{\textbf{WIMPs}}}

\newcommand{\LSP}{\href{https://en.wikipedia.org/wiki/Lightest_supersymmetric_particle}{\textbf{LSP}}}

%%%%% Siglas %%%%

\newcommand{\CMB}{\href{https://en.wikipedia.org/wiki/Cosmic_microwave_background}{\textbf{CMB}}}

\newcommand{\LHC}{\href{https://es.wikipedia.org/wiki/Gran_colisionador_de_hadrones}{\textbf{LHC}}}

\newcommand{\CERN}{\href{https://es.wikipedia.org/wiki/Organizaci\%C3\%B3n_Europea_para_la_Investigaci\%C3\%B3n_Nuclear}{\textbf{CERN}}}

\newcommand{\CMS}{\href{https://en.wikipedia.org/wiki/Compact_Muon_Solenoid}{\textbf{CMS}}}

\newcommand{\ROOT}{\href{https://en.wikipedia.org/wiki/ROOT}{\textbf{ROOT}}}

\newcommand{\MSSM}{\href{https://en.wikipedia.org/wiki/Minimal_Supersymmetric_Standard_Model}{\textbf{MSSM}}}

\newcommand{\WMAP}{\href{https://en.wikipedia.org/wiki/Wilkinson_Microwave_Anisotropy_Probe}{\textbf{WMAP}}}

\newcommand{\ME}{\href{https://es.wikipedia.org/wiki/Modelo_est\%C3\%A1ndar_de_la_f\%C3\%ADsica_de_part\%C3\%ADculas}{\textbf{SM}}}

\newcommand{\MC}{\href{https://en.wikipedia.org/wiki/Monte_Carlo}{\textbf{MC}}}

\newcommand{\LG}{\href{https://es.wikipedia.org/wiki/Fantasma_de_Fadd\%C3\%A9yev-Popov}{lagrangiano fantasma}}

\newcommand{\EW}{\href{https://es.wikipedia.org/wiki/Modelo_electrod\%C3\%A9bil}{\textbf{EW}}}

\newcommand{\QCD}{\href{https://es.wikipedia.org/wiki/Cromodin\%C3\%A1mica_cu\%C3\%A1ntica}{\textbf{QCD}}}

\newcommand{\SUSY}{\href{https://en.wikipedia.org/wiki/Supersymmetry}{\textbf{SUSY}}}