### 2020-06-11 old/Master Thesis Dark SUSY 2020/tex/Chapters/Beyond_Standard_Model/Dark_Matter.tex

Dark matter has become such an established paradigm in modern astroand particle physics that its existence is generally accepted with little explanation. Such blithe and widespread adoption of a cosmology in which an unknown matter plays the pivotal role has led some to become a little sceptical about its existence. It is worth reminding ourselves, from time to time, of the strong and compelling evidence on which this paradigm actually stands. As it so happens, we will also pick up a good deal of information along the way about what properties dark matter must have.